Numerical study of extreme mechanical efforts exerted by a turbulent flow on a bluff body by direct and rare-event sampling techniques

### 2020-02-07 jfm/draft_p2_jfm.tex
Update abstract following Emmanuel's comments

\title{\sout{Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body}
\ZZ{Numerical study of extreme mechanical efforts exerted by a turbulent flow on a bluff body by direct and rare-event sampling techniques}
}

@@

\begin{abstract}
	\ZZ{This study investigates by means of direct numerical simulation, extreme drag events exerted by a  turbulent flow on a bluff body and examine the relevance of statistical algorithms to sample efficiently these events. Two representative algorithms are examined: AMS and GKTL. Briefly mention differences and complementarity. What do we learn? The take-home message is...}
\sout{This study evaluates the relevance of rare-event sampling techniques to accelerate the simulation of extreme mechanical efforts exerted by a turbulent flow impinging onto a bluff body.
The main idea is to replace a long simulation by a set of much shorter ones, running in parallel, with dynamics that are replicated or pruned in order to sample large-amplitude events more frequently.
%
Such techniques have been shown to be efficient for a wide range of problems in statistical physics, computer science, biochemistry, enabling the simulation of rare  events otherwise out of reach by direct sampling.
This work is the first application to fluid-structure interaction problems.
%
The drag experienced by a squared obstacle placed in a turbulent flow (in two dimensions) is taken as a representative case study to investigate the performance of two major rare-event sampling algorithms, namely the \ac{ams} and the \ac{gktl} algorithms.
Practical evidence is given that the fast sweeping-time of fluid structures past the obstacle has a drastic influence on the efficiency of these two algorithms.
While it is shown that the \ac{ams} algorithm does not yield significant run-time savings, the \ac{gktl} algorithm appears to be efficient to sample extreme fluctuations of the time-averaged drag and estimate related statistics such as return times.
%
Beyond the study of applicability of rare-event sampling techniques to a fluid-mechanical problem, this work also includes a detailed phenomenological description of extreme-drag events of a turbulent flow on a bluff body. }
\end{abstract}

>>>>

\title{
  Numerical study of extreme mechanical efforts exerted by a turbulent flow on a bluff body by direct and rare-event sampling techniques
}

@@

\begin{abstract}
  This study investigates, by means of numerical simulations, extreme mechanical efforts exerted by a turbulent flow impinging onto a bluff body, and examines the relevance of statistical algorithms to efficiently sample these events.
  The drag experienced by a squared obstacle placed in a turbulent channel flow (in two dimensions) is taken as a representative case study.
  Direct sampling shows that extreme fluctuations are closely related to the presence of a strong vortex blocked in the near wake of the obstacle.
  Two different algorithms are considered to speed up the sampling of such flow scenarii related to extreme values of the drag, namely the \ac{ams} and the \ac{gktl} algorithms.
  The idea behind these algorithms is to replace a long simulation by a set of much shorter ones, running in parallel, with dynamics that are replicated or pruned to sample large-amplitude events more frequently.
  These two algorithms are representative of the two main class of algorithms applicable to non-equilibrium and deterministic dynamics.
  Whilst the \ac{ams} is general, the \ac{gktl} algorithm is particularly suited to sample trajectories based on the average value of a given observable.
  These algorithms have been shown to be relevant for a wide range of problems in statistical physics, computer science, biochemistry, but it is here the first application to a fluid-structure interaction problem.
  Practical evidence is given that the fast sweeping time of fluid structures past the obstacle has a strong
  influence on the efficiency of the selection-and-cloning rules of these two algorithms. While
  the \ac{ams} algorithm does not yield significant run-time savings as compared to direct
  sampling, the \ac{gktl} algorithm appears to be efficient to sample extreme fluctuations of
  the time-averaged drag and estimate related statistics such as return times.
\end{abstract}
